---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AnVILplot

Color Palettes for AnVIL and the ability to add an AnVIL logo to the bottom right of plots.

Colors are chosen or adapted from [AnVIL style guide](https://anvilproject.org/guides/style/color-palette).

## Installation Instructions

This package can be installed from GitHub using the `devtools` `install_github` function.

```{r}
devtools::install_github("fhdsl/AnVILplot")
```

## To use

Use this package in conjunction with `ggplot2`. You'll need to load both

```{r}
library(AnVILplot)
library(ggplot2)
```

### Adding a logo with `anvil_logo()`

Logos are added to the bottom right of a ggplot.

You can choose between two logos. One is the full AnVIL logo (default, or use argument `full_logo = TRUE`), and the other is just the image of an anvil (use argument `full_logo = FALSE`). 

<details><summary>Logo placement and sizing</summary>


*Logo placement* 

The logo by default is placed on the bottom right of the plot. Use the `x_unit` and `y_unit` arguments to shift the logo placement. 

*Logo sizing*

The defaults for logo width and height are preset to work with the full logo. Adjust the width parameter to be 18 pts as shown in the example at the end of the README.

Note that you may have to adjust both the `height_unit` and `width_unit` arguments to avoid warping the logo/aspect ratio.


</details>

### Palettes Available

#### `anvil_palette_discrete`

This is 2 discrete palettes (`light` and `dark`) with each of those discrete palettes having 4 colors within that group.

```{r}
plot(anvil_palette_discrete)
```

### `anvil_palette_sequential`

This is 3 sequential palettes (`blue`, `yellow`, and `lightgreen`) with each of those sequential palettes having 7 sequential colors within that color group.

```{r}
plot(anvil_palette_sequential)
```

### `anvil_palette_sequential_blues`

This palette has 5 sequential blues.

```{r}
plot(anvil_palette_sequential_blues)
```

### `anvil_palette_diverging`

This palette has 19 colors ranging from dark blue to lighter blue, white, lighter yellows, and dark gray yellows.  

```{r}
plot(anvil_palette_diverging)
```


### `anvil_palette_full`

This is the 9 colors defined in the AnVIL style guide.

```{r}
plot(anvil_palette_full)
```

### `anvil_palette_contrast2`

This is 2 contrasting colors. A blue and a drab yellow. 

```{r}
plot(anvil_palette_contrast2)
```

### `anvil_palette_complement2`

This is 2 complementing colors.A darker blue and a pale turquoise. 

```{r}
plot(anvil_palette_complement2)
```

### `anvil_palette_single`

This one isn't a palette at all, but just a single dark blue picked from the colors.

```{r}
plot(anvil_palette_single)
```

## Example Usage

This base plot uses default coloring (viridis).

```{r}
base_plot <- ggplot(diamonds[sample(nrow(diamonds), 1000), ], 
                    aes(carat, price)) +
             geom_point(aes(colour = cut))

base_plot
```

We can use an AnVIL palette to recolor the graph as shown below. This sequential palette works with the idea of the "cut" ranging from Fair to Ideal.

```{r}
base_plot +
  scale_colour_palette_d(anvil_palette_sequential$yellow)
```

We can also add the AnVIL logo to the bottom right of the plot. By default, it uses the full AnVIL logo (anvil icon and name).

```{r}
base_plot +
  scale_colour_palette_d(anvil_palette_sequential$yellow) +
  anvil_logo()
```

To use a simplified logo (just the AnVIL icon w/o the name), set `full_logo = FALSE` and adjust the `width_unit` argument. 18pt works with the default height.

```{r}
base_plot +
  scale_colour_palette_d(anvil_palette_sequential$yellow) +
  anvil_logo(full_logo = FALSE, width_unit = 18)
```

