---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AnVILplot

Color Palettes for AnVIL and the ability to add an AnVIL logo to the bottom right of plots.

Colors are chosen or adapted from [AnVIL style guide](https://anvilproject.org/guides/style/color-palette).

## Installation Instructions

This package can be installed from GitHub using the `devtools` `install_github` function.

```{r}
devtools::install_github("fhdsl/AnVILplot")
```

## To use

Use this package in conjunction with `ggplot2`. You'll need to load both

```{r}
library(AnVILplot)
library(ggplot2)
```

### Adding a logo with `anvil_logo()`

Logos are added to the bottom right of a ggplot.

You can choose between two logos. One is the full AnVIL logo (default, or use argument `full_logo = TRUE`), and the other is just the image of an anvil (use argument `full_logo = FALSE`). 

### Palettes Available

#### `anvil_palette_discrete`

This is 2 discrete palettes (`light` and `dark`) with each of those discrete palettes having 4 colors within that group.

```{r}
plot(anvil_palette_discrete)
```

### `anvil_palette_sequential`

This is 3 sequential palettes (`blue`, `yellow`, and `lightgreen`) with each of those sequential palettes having 7 sequential colors within that color group.

```{r}
plot(anvil_palette_sequential)
```

### `anvil_palette_sequential_blues`

This palette has 5 sequential blues.

```{r}
plot(anvil_palette_sequential_blues)
```

### `anvil_palette_diverging`

This palette has 19 colors ranging from dark blue to lighter blue, white, lighter yellows, and dark gray yellows.  

```{r}
plot(anvil_palette_diverging)
```


### `anvil_palette_full`

This is the 9 colors defined in the AnVIL style guide.

```{r}
plot(anvil_palette_full)
```

### `anvil_palette_contrast2`

This is 2 contrasting colors. A blue and a drab yellow. 

```{r}
plot(anvil_palette_contrast2)
```

### `anvil_palette_complement2`

This is 2 complementing colors.A darker blue and a pale turquoise. 

```{r}
plot(anvil_palette_complement2)
```

### `anvil_palette_single`

This one isn't a palette at all, but just a single dark blue picked from the colors.

```{r}
plot(anvil_palette_single)
```

## Example Usage

```{r}
ggplot(diamonds[sample(nrow(diamonds), 1000), ], aes(carat, price)) +
geom_point(aes(colour = cut)) +
scale_colour_palette_d(anvil_palette_sequential$yellow) #+
#anvil_logo()

```


